Parallel Global Optimization for Non-Convex Mixed-Integer Problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-06-07 2019/RSD_Integer/RSD2019.tex
After review

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems
\thanks{This study was supported by the Russian Science Foundation, 
project No.\,16-11-10150.}}
\author{Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{ \{konstantin.barkalov,ilya.lebedev\}@itmm.unn.ru}}

@@

This method of organizing parallel computing has the following justification.
The characteristics of intervals $R(i)$ used in the index algorithm can be considered as
probability measures of the global minimum point location in these intervals. Inequalities
(\ref{Eq:23}) arrange intervals according to their characteristics, and trials are carried out in parallel in
the first $p$ intervals with the largest probabilities.
A detailed description of the algorithm convergence theory is presented in \cite{Strongin2000}.

@@

>>>>

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}}
\author{Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{ \{konstantin.barkalov,ilya.lebedev\}@itmm.unn.ru}}

@@

This method of organizing parallel computing has the following justification.
The characteristics of intervals $R(i)$ used in the index algorithm can be considered as
probability measures of the global minimum point location in these intervals. Inequalities
(\ref{Eq:23}) arrange intervals according to their characteristics, and trials are carried out in parallel in
the first $p$ intervals with the largest probabilities.
A detailed description of the algorithm convergence theory is presented in \cite{Strongin2000}.
The results of comparison of the algorithm with other sequential and parallel global optimization algorithms have been presented in \cite{Sovrasov2019}.

@@

\bibitem{Sovrasov2019}
Sovrasov, V., Bevzuk, S.: Comparison of several sequential and parallel derivative-free global optimization algorithms. 	Communications in Computer and Information Science (2019) (article in press)
